Proceedings of the OHBM Hackathon 2023

### 2025-03-12 manuscript/affiliations.tex
enh: add text, affiliations, abstract, keywords etc

\affil[1]{Division of Experimental Psychology and Neuropsychology, Department of Education and Psychology, Freie Universität Berlin}
\affil[2]{Department of Psychology, Center for Perceptual Systems, The University of Texas at Austin}
\affil[3]{Centre for Sleep and Cognition & Centre for Translational Magnetic Resonance Research, Yong Loo Lin School of Medicine, National University of Singapore, Singapore}
\affil[4]{Department of Psychiatry, The University of Melbourne and Melbourne Health, Victoria, Australia}
\affil[5]{Shanghai Mental Health Center, School of Medicine, Shanghai Jiao Tong University, 600 S. Wanping Rd., Shanghai, 200030}
\affil[6]{Department of Psychology, Faculty of Arts and Social Science, University of Zurich, Zurich, ZH, Switzerland}
\affil[7]{School of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta, Georgia, United States}
\affil[8]{Department of Cognitive Neuroscience, Faculty of Psychology and Neuroscience, Maastricht University, Maastricht, The Netherlands}
\affil[9]{School of Physics, The University of Sydney, Sydney, Australia}
\affil[10]{Big Data Institute, University of Oxford, UK}
\affil[11]{Univ Rennes, Inria, CNRS, Inserm, Rennes, France}
\affil[12]{Department of Radiology, Lausanne University Hospital and University of Lausanne, Lausanne, VD, Switzerland.}
\affil[13]{Robarts Research Institute, Western University, London, Ontario, Canada}
\affil[14]{School of Psychological Sciences, College of Engineering, Science and Environment, University of Newcastle, Newcastle, NSW, Australia}
\affil[15]{Hunter Medical Research Institute, Newcastle, NSW, Australia}
\affil[16]{Speech and Hearing Bioscience and Technology, Harvard University, USA}
\affil[17]{Campbell Family Mental Health Research Institute, Centre for Addiction and Mental Health, Toronto, ON, Canada}
\affil[18]{Northwestern University, Evanston, USA}
\affil[19]{Department of Bioengineering, McGill University, Montreal, QC, Canada}
\affil[20]{Paris Brain Institute}
\affil[21]{Department of Radiography, Faculty of Health and Social Sciences, Western Norway University of Applied Sciences, Bergen, Norway}
\affil[22]{Centre de recherche de l'Institut universitaire de gériatrie de Montréal, Montréal, QC, Canada}
\affil[23]{Brain Innovation, Maastricht, The Netherlands}
\affil[24]{National Institutes of Health, Bethesda, MD, USA}
\affil[25]{Department of Biomedical Engineering, Vanderbilt University}
\affil[26]{Danish Research Centre for Magnetic Resonance, Centre for Functional and Diagnostic Imaging and Research, Copenhagen University Hospital - Amager and Hvidovre, Copenhagen, Denmark}
\affil[27]{Melbourne Neuropsychiatry Centre, Department of Psychiatry, The University of Melbourne and Melbourne Health, Victoria, Australia}
\affil[28]{Neuro-X Institute, École polytechnique fédérale de Lausanne, Geneva, Switzerland}
\affil[29]{Department of Radiology and Medical Informatics (DRIM), Faculty of Medicine, University of Geneva, Geneva, Switzerland}
\affil[30]{Department of Cognitive Neuroscience, Faculty of Psychology and Neuroscience, Maastricht University, Maastricht, The Netherlands}
\affil[31]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, Old Road Campus, Oxford, OX3 7LF, UK}
\affil[32]{Fetal Neonatal Neuroimaging and Developmental Science Center, Boston Children’s Hospital, Harvard Medical School, Boston, MA, United States}
\affil[33]{Organization for Human Brain Mapping, USA}

>>>>

\affil[1]{Division of Experimental Psychology and Neuropsychology, Department of Education and Psychology, Freie Universität Berlin}
\affil[2]{Department of Psychology, Center for Perceptual Systems, The University of Texas at Austin, Austin, Texas, United States}
\affil[3]{Centre for Sleep and Cognition & Centre for Translational Magnetic Resonance Research, Yong Loo Lin School of Medicine, National University of Singapore, Singapore}
\affil[4]{Department of Psychiatry, The University of Melbourne and Melbourne Health, Victoria, Australia}
\affil[5]{Shanghai Mental Health Center, School of Medicine, Shanghai Jiao Tong University, Shanghai, China}
\affil[6]{Department of Psychology, Faculty of Arts and Social Science, University of Zurich, Zurich, Switzerland}
\affil[7]{School of Electrical and Computer Engineering, Georgia Institute of Technology, Atlanta, Georgia, United States}
\affil[8]{Department of Cognitive Neuroscience, Faculty of Psychology and Neuroscience, Maastricht University, Maastricht, The Netherlands}
\affil[9]{School of Physics, The University of Sydney, Sydney, Australia}
\affil[10]{Big Data Institute, University of Oxford, United Kingdom}
\affil[11]{Univ Rennes, Inria, CNRS, Inserm, Rennes, France}
\affil[12]{Department of Radiology, Lausanne University Hospital and University of Lausanne, Lausanne, Switzerland}
\affil[13]{Robarts Research Institute, Western University, London, Canada}
\affil[14]{School of Psychological Sciences, College of Engineering, Science and Environment, University of Newcastle, Newcastle, Australia}
\affil[15]{Hunter Medical Research Institute, Newcastle, Australia}
\affil[16]{Speech and Hearing Bioscience and Technology, Harvard University, Cambridge, United States}
\affil[17]{Campbell Family Mental Health Research Institute, Centre for Addiction and Mental Health, Toronto, Canada}
\affil[18]{Northwestern University, Evanston, United States}
\affil[19]{Department of Bioengineering, McGill University, Montreal, Canada}
\affil[20]{Paris Brain Institute, Paris, France}
\affil[21]{Department of Radiography, Faculty of Health and Social Sciences, Western Norway University of Applied Sciences, Bergen, Norway}
\affil[22]{Centre de recherche de l'Institut universitaire de gériatrie de Montréal, Montréal, Canada}
\affil[23]{Brain Innovation, Maastricht, The Netherlands}
\affil[24]{National Institutes of Health, Bethesda, United States}
\affil[25]{Department of Biomedical Engineering, Vanderbilt University, Nashville, United States}
\affil[26]{Danish Research Centre for Magnetic Resonance, Department of Radiology and Nuclear Medicine, Copenhagen University Hospital - Amager and Hvidovre, Copenhagen, Denmark}
\affil[27]{Melbourne Neuropsychiatry Centre, Department of Psychiatry, The University of Melbourne and Melbourne Health, Victoria, Australia}
\affil[28]{Neuro-X Institute, École polytechnique fédérale de Lausanne, Geneva, Switzerland}
\affil[29]{Department of Radiology and Medical Informatics (DRIM), Faculty of Medicine, University of Geneva, Geneva, Switzerland}
\affil[30]{Department of Cognitive Neuroscience, Faculty of Psychology and Neuroscience, Maastricht University, Maastricht, The Netherlands}
\affil[31]{Big Data Institute, Li Ka Shing Centre for Health Information and Discovery, Oxford, United Kingdom}
\affil[32]{Fetal Neonatal Neuroimaging and Developmental Science Center, Boston Children’s Hospital, Harvard Medical School, Boston, United States}
\affil[33]{Organization for Human Brain Mapping, Roseville, United States}
\affil[34]{Systems Lab, Department of Psychiatry, The University of Melbourne, Melbourne, Victoria, Australia}
\affil[35]{Department of Biomedical Engineering, The University of Melbourne, Melbourne, Victoria, Australia}

### 2025-03-12 manuscript/main.tex
enh: add text, affiliations, abstract, keywords etc

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{natbib}
\usepackage[table,xcdraw]{xcolor}
\usepackage{hyperref}

@@

\title{Proceedings of the OHBM Hackathon 2023}

@@

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.99\textwidth]{images/demographics.png}
    \label{fig:demographics}
    \caption{
        The four panels illustrate key demographic and participation trends for the OHBM BrainHack 2023 participants.
        \textbf{Panel A} shows the geographic distribution, with Canada, the United States, and France as the most represented countries among 13 in total.
        \textbf{Panel B} presents the career status distribution, with Early Career Researchers (ECRs)—including PhD students and postdoctoral researchers—making up half of the attendees, followed by established faculty (31.2\%) and Master's students (12.5\%).
        \textbf{Panel C} depicts participant satisfaction ratings for sessions such as Unconference, TrainTrack, and HackTrack, showing higher satisfaction for HackTrack sessions overall.
        \textbf{Panel D} examines format preferences (hybrid vs. onsite), with a stronger preference for hybrid participation among ECRs and attendees with more prior experience at BrainHack events, while onsite preference was higher among established faculty.
    }
\end{figure}

@@

\begin{table}[]
    \begin{tabular}{|l|l|c|}

@@

    \multicolumn{1}{|c|}{\textbf{Topic}}        & \multicolumn{1}{|c|}{\textbf{Session}}         & \multicolumn{1}{|c|}{\textbf{Link}}                                                                                                 \\ \hline
    \textbf{Getting started}                    & Setting-up a hack friendly environment         & \href{https://psy6983.brainhackmtl.org/modules/installation/}{Link}                                                      \\ \hline
                                                & Intro to jupyter notebooks                     & \href{https://docs.jupyter.org/en/latest/start/index.html}{Link}                                                         \\ \cline{2-3} 
                                                & Intro to bash                                  & \href{https://psy6983.brainhackmtl.org/modules/introduction\_to\_terminal/}{Link}                                        \\ \cline{2-3} 
                                                & Python: Data analysis                          & \href{https://psy6983.brainhackmtl.org/modules/python\_data\_analysis/}{Link}                                            \\ \cline{2-3} 
                                                & Python: Visualisation                          & \href{https://psy6983.brainhackmtl.org/modules/python\_visualization/}{Link}                                             \\ \cline{2-3} 
                                                & Python: Writing a script                       & \href{https://psy6983.brainhackmtl.org/modules/python\_scripts/}{Link}                                                   \\ \cline{2-3} 
    \multirow{-6}{*}{\textbf{Coding skills}}    & Python: Packaging (pipy)                       & \href{https://psy6983.brainhackmtl.org/modules/packaging/}{Link}                                                         \\ \hline
                                                & Using Git and Github                           & \href{https://youtu.be/zh\_WFv0uk7w}{Link} \href{https://psy6983.brainhackmtl.org/modules/git\_github/}{Link} \\ \cline{2-3} 
                                                & Data management with Datalad                   & \href{https://psy6983.brainhackmtl.org/modules/datalad/}{Link} \href{https://youtu.be/QsAqnP7TwyY}{Link}      \\ \cline{2-3} 
    \multirow{-5}{*}{\textbf{Version control}}  & Containers for science                         & \href{https://youtu.be/pc3YOZUG3lQ}{Link}                                                                                \\ \hline
                                                & How to write good code                         & \href{https://youtu.be/gfPP2pQ8Rms}{Link}                                                                                \\ \cline{2-3} 
                                                & Reproducible workflows: The Turing Way         & \href{https://youtu.be/tk2eZSrM8oA}{Link}                                                                                \\ \cline{2-3} 
    \multirow{-3}{*}{\textbf{Good practices}}   & Reproducible workflows: Transparent MRI        & \href{https://youtu.be/dSOQgyuL51U}{Link}                                                                                \\ \hline
                                                & Machine Learning basics                        & \href{https://psy6983.brainhackmtl.org/modules/machine\_learning\_basics/}{Link}                                         \\ \cline{2-3} 
                                                & Machine Learning for neuroimaging              & \href{https://psy6983.brainhackmtl.org/modules/machine\_learning\_neuroimaging/}{Link}                                   \\ \cline{2-3} 
    \multirow{-3}{*}{\textbf{Machine learning}} & Machine Learning Reproducibility Checklist     & \href{https://www.cs.mcgill.ca/$\sim$jpineau/ReproducibilityChecklist.pdf}{Link}                                         \\ \hline

@@

The Buddy System was established to support and engage newcomers at the Hackathon.
This initiative pairs participants in a mentor-mentee fashion, with mentors guiding interests, projects to join, and networking opportunities throughout the Hackathon.
Introduced in the previous 2022 edition, the system was refined for 2023 to create a more dynamic and natural community structure (see Figure \ref{fig:buddy-system}).
Pairs were given the freedom to choose their buddies to avoid any biases in matching, ensuring a fair and supportive environment for all participants.
In doing so, first-time attendees and more experienced brainhackers were encouraged to network and get to know each other while also sharing information about what to expect from the brainhack.
This system has been instrumental in helping first-time attendees feel welcomed and integrated into the community.

\begin{figure}[h]
    \centering
    \includegraphics[width=0.99\textwidth]{images/buddy-system.png}
    \label{fig:buddy-system}
    \caption{
        (a) Front, and (b) back of a buddy card.
        Buddy cards were distributed amongst all attendees who expressed interest in participating in the refined dynamic buddy system.
        Individualized who participated were asked to share their cards with other brainhackers during lunch and coffee breaks.
        The cards acted as catalist to start a conversation and exchange thoughts, experiences, and contact information.
    }
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{images/clinica.png}
    \label{fig:clinica}
    \caption{
        Scatterplot of HD BET Dice probability and correlation ratio between reference and moving images. Red color means both metrics are below the threshold, blue or purple means one of the metrics is below the threshold, green means both metrics are above the threshold.
    }
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.8\textwidth]{images/cerebro.png}
    \label{fig:cerebro}
    \caption{
        Cerebro – A Python-Based 3D Brain Visualization Tool. (a) Cerebro leverages an extensive array of open-source Python tools, forming a robust foundation for its functionality. It also integrates with these tools to enable seamless Pythonic neuroimaging visualizations. (b) Cerebro prioritizes principles of scriptability, reproducibility, visualization quality, cross-compatibility, and integration in its pursuit of providing a reliable solution for the neuroimaging community. (c) An illustrative Cerebro-generated visualization, accompanied by a scannable QR code linked to the publicly accessible reproduction scripts.
    }
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth]{images/k-particles.png}
    \label{fig:kparticles}
    \caption{
        Our compilation of k-space animations generated during the brainhack can be seen at \href{https://youtu.be/XS0LEQExGU8?si=I5Zufp3AcCbdhYIR}{YouTube}.
    }
\end{figure}

@@

\begin{figure}[h]
    \centering
    \includegraphics[width=0.9\textwidth]{images/skull.png}
    \label{fig:skull}
    \caption{
        Skull sculpture generated using MidJourney's generative models for the main website and 3D printed replica for the Rhyming Battle winner. 
    }
\end{figure}

>>>>

\documentclass{article}
\usepackage[utf8]{inputenc}
\usepackage{authblk}
\usepackage{graphicx}
\usepackage{multirow}
\usepackage{natbib}
\usepackage[table,xcdraw]{xcolor}
\usepackage{hyperref}
\usepackage{float}
\usepackage[T1]{fontenc}

\interlinepenalty=1000

@@

\title{Proceedings of the OHBM Hackathon 2023}
\date{}

@@

\begin{abstract}
    The OHBM Brainhack 2023 integrated educational innovation, creative expression, and scientific exploration to cultivate a dynamic and inclusive environment for learning and collaboration. The event featured two main components: the Train-Track, which provided structured and flexible hands-on training in a study group setting, and the Hack-Track, where participants engaged in open-source project development. To enhance engagement, the Buddy System facilitated peer support, ensuring newcomers felt welcomed within the Brainhack community. A novel addition to this year’s event was the Rhyming Battle, which encouraged participants to creatively express their experiences through scientific humor and artistic wordplay. Additionally, the introduction of the Mini-Grant Initiative aimed to recognize projects that prioritized open science, diversity, and interdisciplinary collaboration. While this initiative received mixed feedback due to its competitive nature, it provided valuable insights for future iterations. Here we reflect on the successes and lessons learned from Brainhack 2023, underscoring the collective impact of these initiatives.
\end{abstract}

\textbf{\textit{Keywords:}} Open Science, Brainhack, Hackathon, Neuroimaging, Neuroscience

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.99\textwidth]{images/demographics.png}
    \caption{
        The four panels illustrate key demographic and participation trends for the OHBM BrainHack 2023 participants.
        \textbf{Panel A} shows the geographic distribution, with Canada, the United States, and France as the most represented countries among 13 in total.
        \textbf{Panel B} presents the career status distribution, with Early Career Researchers (ECRs)—including PhD students and postdoctoral researchers—making up half of the attendees, followed by established faculty (31.2\%) and Master's students (12.5\%).
        \textbf{Panel C} depicts participant satisfaction ratings for sessions such as Unconference, TrainTrack, and HackTrack, showing higher satisfaction for HackTrack sessions overall.
        \textbf{Panel D} examines format preferences (hybrid vs. onsite), with a stronger preference for hybrid participation among ECRs and attendees with more prior experience at BrainHack events, while onsite preference was higher among established faculty.
    }
    \label{fig:demographics}
\end{figure}

\pagebreak

@@

\begin{table}[H]
    \begin{tabular}{@{}|l|l|@{}}

@@

    \multicolumn{1}{|c|}{\textbf{Topic}} & \multicolumn{1}{c|}{\textbf{Session}}                                                                                                                                                           \\ \hline
    \textbf{Getting started}             & \begin{tabular}[c]{@{}l@{}}Setting-up a hack friendly environment     \\ \texttt{https://psy6983.brainhackmtl.org/modules/installation/}                                          \end{tabular} \\ \cline{2-2}
                                         & \begin{tabular}[c]{@{}l@{}}Intro to jupyter notebooks                 \\ \texttt{https://docs.jupyter.org/en/latest/start/index.html}                                             \end{tabular} \\ \cline{2-2}
                                         & \begin{tabular}[c]{@{}l@{}}Intro to bash                              \\ \texttt{https://psy6983.brainhackmtl.org/modules/introduction\_to\_terminal/}                            \end{tabular} \\ \cline{2-2}
                                         & \begin{tabular}[c]{@{}l@{}}Python: Data analysis                      \\ \texttt{https://psy6983.brainhackmtl.org/modules/python\_data\_analysis/}                                \end{tabular} \\ \cline{2-2}
                                         & \begin{tabular}[c]{@{}l@{}}Python: Visualisation                      \\ \texttt{https://psy6983.brainhackmtl.org/modules/python\_visualization/}                                 \end{tabular} \\ \cline{2-2}
                                         & \begin{tabular}[c]{@{}l@{}}Python: Writing a script                   \\ \texttt{https://psy6983.brainhackmtl.org/modules/python\_scripts/}                                       \end{tabular} \\ \hline
     \textbf{Coding skills}              & \begin{tabular}[c]{@{}l@{}}Python: Packaging (pipy)                   \\ \texttt{https://psy6983.brainhackmtl.org/modules/packaging/}                                             \end{tabular} \\ \cline{2-2}
                                         & \begin{tabular}[c]{@{}l@{}}Using Git and Github                       \\ \texttt{https://youtu.be/zh\_WFv0uk7w} \\ \texttt{https://psy6983.brainhackmtl.org/modules/git\_github/} \end{tabular} \\ \cline{2-2}
                                         & \begin{tabular}[c]{@{}l@{}}Data management with Datalad               \\ \texttt{https://psy6983.brainhackmtl.org/modules/datalad/} \\ \texttt{https://youtu.be/QsAqnP7TwyY}      \end{tabular} \\ \hline
    \textbf{Version control}             & \begin{tabular}[c]{@{}l@{}}Containers for science                     \\ \texttt{https://youtu.be/pc3YOZUG3lQ}                                                                    \end{tabular} \\ \cline{2-2}
                                         & \begin{tabular}[c]{@{}l@{}}How to write good code                     \\ \texttt{https://youtu.be/gfPP2pQ8Rms}                                                                    \end{tabular} \\ \cline{2-2}
                                         & \begin{tabular}[c]{@{}l@{}}Reproducible workflows: The Turing Way     \\ \texttt{https://youtu.be/tk2eZSrM8oA}                                                                    \end{tabular} \\ \hline
    \textbf{Good practices}              & \begin{tabular}[c]{@{}l@{}}Reproducible workflows: Transparent MRI    \\ \texttt{https://youtu.be/dSOQgyuL51U}                                                                    \end{tabular} \\ \cline{2-2}
                                         & \begin{tabular}[c]{@{}l@{}}Machine Learning basics                    \\ \texttt{https://psy6983.brainhackmtl.org/modules/machine\_learning\_basics/}                             \end{tabular} \\ \cline{2-2}
                                         & \begin{tabular}[c]{@{}l@{}}Machine Learning for neuroimaging          \\ \texttt{https://psy6983.brainhackmtl.org/modules/machine\_learning\_neuroimaging/}                       \end{tabular} \\ \hline
    \textbf{Machine learning}            & \begin{tabular}[c]{@{}l@{}}Machine Learning Reproducibility Checklist \\ \texttt{https://www.cs.mcgill.ca/$\sim$jpineau/ReproducibilityChecklist.pdf}                             \end{tabular} \\ \hline

@@

The Buddy System was established to support and engage newcomers at the Hackathon.
This initiative pairs participants in a mentor-mentee fashion, with mentors guiding interests, projects to join, and networking opportunities throughout the Hackathon.
Introduced in the previous 2022 edition, the system was refined for 2023 to create a more dynamic and natural community structure (see Figure \ref{fig:buddy-system}).

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.99\textwidth]{images/buddy-system.png}
    \label{fig:buddy-system}
    \caption{
        (a) Front, and (b) back of a buddy card.
        Buddy cards were distributed amongst all attendees who expressed interest in participating in the refined dynamic buddy system.
        Individualized who participated were asked to share their cards with other brainhackers during lunch and coffee breaks.
        The cards acted as catalist to start a conversation and exchange thoughts, experiences, and contact information.
    }
\end{figure}

Pairs were given the freedom to choose their buddies to avoid any biases in matching, ensuring a fair and supportive environment for all participants.
In doing so, first-time attendees and more experienced brainhackers were encouraged to network and get to know each other while also sharing information about what to expect from the brainhack.
This system has been instrumental in helping first-time attendees feel welcomed and integrated into the community.

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.8\textwidth]{images/clinica.png}
    \label{fig:clinica}
    \caption{
        Scatterplot of HD BET Dice probability and correlation ratio between reference and moving images. Red color means both metrics are below the threshold, blue or purple means one of the metrics is below the threshold, green means both metrics are above the threshold.
    }
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.8\textwidth]{images/cerebro.png}
    \label{fig:cerebro}
    \caption{
        Cerebro – A Python-Based 3D Brain Visualization Tool. (a) Cerebro leverages an extensive array of open-source Python tools, forming a robust foundation for its functionality. It also integrates with these tools to enable seamless Pythonic neuroimaging visualizations. (b) Cerebro prioritizes principles of scriptability, reproducibility, visualization quality, cross-compatibility, and integration in its pursuit of providing a reliable solution for the neuroimaging community. (c) An illustrative Cerebro-generated visualization, accompanied by a scannable QR code linked to the publicly accessible reproduction scripts.
    }
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.9\textwidth]{images/k-particles.png}
    \label{fig:kparticles}
    \caption{
        Our compilation of k-space animations generated during the brainhack can be seen at \href{https://youtu.be/XS0LEQExGU8?si=I5Zufp3AcCbdhYIR}{YouTube}.
    }
\end{figure}

@@

\begin{figure}[hbt!]
    \centering
    \includegraphics[width=0.9\textwidth]{images/skull.png}
    \label{fig:skull}
    \caption{
        Skull sculpture generated using MidJourney's generative models for the main website and 3D printed replica for the Rhyming Battle winner.
    }
\end{figure}
